\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-16 Paper/paper.tex
Testing Frameworks edits

\subsubsection{Selenium\cite{Selenium}}
Selenium is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On it's own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

Generally, all browser testing tools will be using Selenium behind the scenes and doing the housekeeping automatically. This is the case for both of the web testing tools that will follow this description.

Selenium has support for running a number of different browsers.

@@

Selenium's node incarnation is out-of-date and as such we had to change the selenium package to use the latest version of Selenium that works with the latest version of browsers. This required us to edit some of the JavaScript files that ran Selenium from the console using node. At the time of this writing, the Selenium node package was using Selenium 2.20 from over two years ago. The latest Selenium version is 2.40.

@@

Nightwatch is Node.js module, and as such can easily installed and run via npm and the command-line.

@@

\subsubsection{MagnumCI \cite{MagnumCI}}
MagnumCI is another online CI, it appears that Jenkins is one of the only ``off-line'' CI systems. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects, and that's what we care about.

@@

\subsection{Misc Frameworks}
In addition to the Unit Testing, Continuous Integration, and Browser Testing frameworks outlined above, we came across a number of incredibly helpful frameworks that didn't quite fit into any of the above categories.

@@

\subsection{Misc Tools}
\subsubsection{Node Inspector\cite{NodeInspector}}
Node Inspector is a GitHub project for debugging Node.js server-side code. The inspector runs in the browser and is started by running \lstinline{node-debug} instead of \lstinline{node} when starting the application. Simple as that. Then you can set breakpoints using the normal browser developer tools.

>>>>

\subsubsection{Selenium\cite{Selenium}}
Selenium is an automated browser input runner. It is one of the only automated browser runners and certainly the most prominent. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

Generally, all browser testing tools will be using Selenium behind the scenes and doing the housekeeping automatically. This is the case for the web testing tools that will follow this description.

Selenium has support for running a number of different browsers. Out of the box it comes with support for Firefox but getting Chrome and Safari running takes minimal effort.

@@

Selenium's Node incarnation is out-of-date and as such we had to change the Selenium package to use the latest version of Selenium that works with the latest version of browsers. This required us to edit some of the JavaScript files that ran Selenium from the console using Node. At the time of this writing, the Selenium node package was using Selenium 2.20 from over two years ago. The latest Selenium version is 2.40.

@@

Nightwatch is a Node.js module, and as such can easily installed and run via npm and the commandline.

@@

\subsubsection{MagnumCI \cite{MagnumCI}}
MagnumCI is another online CI framework, it appears that Jenkins is one of the only ``off-line'' CI systems. MagnumCI has every feature available for free, however, it's still in public beta and although prices haven't been released, the team making MagnumCI has already stated that there will be price tiers. It is not unreasonable, though, to believe that MagnumCI will be free for open-source projects, and that's what we care about.

@@

\subsection{Misc Frameworks}
In addition to the Unit Testing, Continuous Integration, and Browser Testing frameworks outlined above, we came across a number of incredibly helpful frameworks that did not quite fit into any of the above categories.

@@

\subsubsection{Node Inspector\cite{NodeInspector}}
Node Inspector is a GitHub project for debugging Node.js server-side code. The inspector runs in the browser and is started by running \lstinline{node-debug} instead of \lstinline{node} when starting the application. Simple as that. Then you can set breakpoints using the normal browser developer tools.
